Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-02-22 article.tex
some details about graph colors added

\begin{figure*}
	\includegraphics[width=\linewidth]{images/SarrafParkinsonTestResult}
	\caption{Parkinson's disease diagnosis accuracy and loss using Sarraf and Tofighi's algorithm.}
	\label{fig:SarrafParkinsonTestResult}
\end{figure*}

@@

As we can see, the proposed method has shown huge success in the task of Parkinson's disease diagnosis in an affordable time. Also, the fascinating point about the experiments is the average mean time-slice accuracy, which is around $92.96\%$. Accordingly, it means the model is able to judge only by a single time-slice of the brain while the prediction is acceptably accurate. We mostly care about the average mean accuracy, which is the average accuracy of the disease diagnosis task and as long as the whole process can predict someone's health situation precisely, we can ignore the time-slice based results. So, we should mostly focus on average mean accuracy and use that to compare the proposed method to other models. Experiment results can be seen in Tables \ref{table:tests_1} to \ref{table:tests_8} and Figures \ref{fig:tests_1} to  \ref{fig:tests_8}.

@@

			\multicolumn{2}{|r|}{Time-slice NPV} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{NPV} & 
			\multicolumn{2}{c|}{ 1 } \\ \hline
		\end{tabular}
	}
	\label{table:tests_1}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_1}
	\caption{Experiment 1. Accuracy and loss of network for training and validation data. Accuracy is based on validation data and loss diagram contains train data loss in blue and validation loss in orange.}
	\label{fig:tests_1}
\end{figure}

>>>>

\begin{figure*}
	\includegraphics[width=\linewidth]{images/SarrafParkinsonTestResult}
	\caption{Parkinson's disease diagnosis accuracy and loss using Sarraf and Tofighi's algorithm. Transparent graphs show practical values and opaque graphs are the result of Linear Smoothing ($\alpha = 0.7$)}
	\label{fig:SarrafParkinsonTestResult}
\end{figure*}

@@

As we can see, the proposed method has shown huge success in the task of Parkinson's disease diagnosis in an affordable time. Also, the fascinating point about the experiments is the average mean time-slice accuracy, which is around $92.96\%$. Accordingly, it means the model is able to judge only by a single time-slice of the brain while the prediction is acceptably accurate. We mostly care about the average mean accuracy, which is the average accuracy of the disease diagnosis task and as long as the whole process can predict someone's health situation precisely, we can ignore the time-slice based results. So, we should mostly focus on average mean accuracy and use that to compare the proposed method to other models. Experiment results can be seen in Tables \ref{table:tests_1} to \ref{table:tests_8} and Figures \ref{fig:tests_1} to  \ref{fig:tests_8}. Transparent graphs show practical values and opaque graphs are the result of Linear Smoothing ($\alpha = 0.7$)

@@

			\multicolumn{2}{|r|}{Time-slice NPV} & 
			\multicolumn{2}{c|}{ 1 } &
			\multicolumn{2}{|r|}{NPV} & 
			\multicolumn{2}{c|}{ 1 } \\ \hline
		\end{tabular}
	}
	\label{table:tests_1}
\end{table}
\begin{figure}
	\includegraphics[width=\linewidth]{images/tests_1}
	\caption{Experiment 1. Accuracy and loss of network for training and validation data. Accuracy is based on validation data and loss diagram contains train data loss in blue and validation loss in orange. Transparent graphs show practical values and opaque graphs are the result of Linear Smoothing ($\alpha = 0.7$)}
	\label{fig:tests_1}
\end{figure}
